Title Goes Here

### 2020-06-12 analysis/paper/paper.Rmd
expand results section

In the SAA data we found a total of `r prettyNum(SAA18_row, big.mark = ",")` presentations. Of these we could identify the first-named author of `r count_gendered_SAA18` (`r perc_gendered_SAA18`%) presentations as either men (n=`r male_count_SAA18`) or women (n=`r female_count_SAA18`). For the CAA meeting we have `r prettyNum(CAA18_row, big.mark = ",")` presentations, and `r count_gendered_CAA18` (`r perc_gendered_CAA18`%) first-named authors could be classified as either men (n=`r male_count_CAA18`) or women (n=`r female_count_CAA18`). For the EAA data we have `r prettyNum(EAA18_row, big.mark = ","` presentations, and `r count_gendered_EAA18` (`r perc_gendered_EAA18`%) where the first author could be classified as either a man (n=`r male_count_EAA18`) or woman (n=`r female_count_EAA18`). This results in similar women-to-men ratios for the SAA (`r female_to_male_SAA18`) and EAA (`r female_to_male_EAA18`), but much lower for the CAA (`r female_to_male_CAA18`).

In the SAA presentations we identified the optimum number of topics as `r SAA_stm_topic_number`, with `r SAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. One of the main difference that we can see between the topics of the genders are the locations that the presenters are interested in. Women are more likely to have a topic at a specific region such as Mesoamerica, Arizona and national parks, while men are more likely to have a topic that are in the western regions.

For EAA we generated a total of `r EAA_stm_topic_number` topics, with `r EAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Although topics significantly associated with men and women both include the word "Mediterranean", it is important to distinguish that females seems to be focusing on western Mediterranean while males seems to be focusing on northern Mediterranean. Another difference is that males tends to have topics that are related to architecture, while the topic regarding research methods using isotopes seems to be more popular for females.

For CAA we generated a total of `r CAA_stm_topic_number` topics, with `r CAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. In CAA's stm topic plot we can see a clearer pattern from the topics marked in red. For females from CAA, we see that topics that are associated with Geographic Information System (GIS) are more likely to be a topic for female presenters. Another female-associated topics from the CAA topic plot is topics that includes the word women, excav and inform. As for males from CAA, there doesn't seem to have a specific word that is more associated with males besides the word enviorn.

@@

>>>>

In the SAA data we found a total of `r prettyNum(SAA18_row, big.mark = ",")` presentations. Of these we could identify the first-named authors of `r count_gendered_SAA18` (`r perc_gendered_SAA18`%) presentations as either men (n=`r male_count_SAA18`) or women (n=`r female_count_SAA18`). In the SAA presentations we identified the optimum number of topics as `r SAA_stm_topic_number`, with `r SAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Eight of these topics were associated with men, and nine topics associated with women. One of the main difference that we can see between the topics of the genders are the locations that the presenters are interested in.  Topics associated more with women include bioarchaeology, cemeteries, burials, shells, and ceramics. Topics associated more with men include survey and landscape archaeology, geoarchaeology, rituals, and regional studies. Women are more likely to work on locations such as Mesoamerica, Arizona and national parks, while men are more likely to have a topics about the Great Lakes, and Honduras.

For the EAA data we have `r prettyNum(EAA18_row, big.mark = ","` presentations, and `r count_gendered_EAA18` (`r perc_gendered_EAA18`%) where the first author could be classified as either a man (n=`r male_count_EAA18`) or woman (n=`r female_count_EAA18`). For EAA we generated a total of `r EAA_stm_topic_number` topics, with `r EAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Seven of these topics were associated with men, and nine topics associated with women. Although topics significantly associated with men and women both include the word "Mediterranean", women seems to be focusing more on the western Mediterranean while men seems to be focusing on the northern Mediterranean. Topics associated more with women include burials, graves, museums, animals, diet, and ritual. Topics associated more with men include geoarchaeology, architecture, and towns.

For the CAA meeting we have `r prettyNum(CAA18_row, big.mark = ",")` presentations, and `r count_gendered_CAA18` (`r perc_gendered_CAA18`%) first-named authors could be classified as either men (n=`r male_count_CAA18`) or women (n=`r female_count_CAA18`). For CAA we generated a total of `r CAA_stm_topic_number` topics, with `r CAA_stm_topic_number_significant_covary` of these showing non-random co-variance with the gender of the first-named presenter. Three of these topics were associated with men, and three topics associated with women. Topics associated more with women include archives, GIS, geophysics, collaboration, and teaching. Topics associated more with men include environmental and landscape archaeology.

@@

This results in similar women-to-men ratios for the SAA (`r female_to_male_SAA18`) and EAA (`r female_to_male_EAA18`), but much lower for the CAA (`r female_to_male_CAA18`).

Compare topics between the three confs
